GMSE: a general tool for management strategy evaluation

### 2019-01-03 notebook/presentation/GMSE_presentation.Rmd
Remove unnecessary explanation of genetic algorithm

@@

<!---
1. Know what to say about the Welikia project

<!---
https://welikia.org/
http://ngm.nationalgeographic.com/2009/09/manhattan/miller-text
https://welikia.org/explore/mannahatta-map/

@@

@@

<!--- 
    START OF THE GENETIC ALGORITHM SET OF SLIDES  ------------------------------
--->

@@

<!--- 
    END OF THE GENETIC ALGORITHM SET OF SLIDES  --------------------------------
--->

>>>>

<style type="text/css">
body p {
  color: #000000;
}
ul {
  color: black;
}
ol {
  color: black;
}
a {
    color: darkblue;
    text-decoration: none
}
.fifty {
   font-size: 50%;
   }
.seventy {
   font-size: 70%;
   }
slides > slide.backdrop {
  background: none !important;
  background-color: white !important;
}
slides > slide.title-slide hgroup h1 {
  color: black;
}
slides > slide.title-slide p {
  color: black;
}
slides > slide.light > hgroup h2 {
  color: black;
}
slides > slide.light > hgroup h1 {
  color: black;
}
ul {
  color: black;
}
ol {
  color: black;
}
p {
  color: black
}
h1, h2, h3, h4, h5, h6, h7, h8, p {
    color: black;
}
.checkbox-inline, .radio-inline {
    margin-right: 90px;
}
.forceBreak { -webkit-column-break-after: always; break-after: column; }
</style>

@@

<!---
1. Know what to say about the Welikia project
--->

<!---
https://welikia.org/
http://ngm.nationalgeographic.com/2009/09/manhattan/miller-text
https://welikia.org/explore/mannahatta-map/
--->

@@

<!---

@@

@@

<!---
